Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-11 manuscript/tables&figures.Rmd
update Table 3
#139
update tables and figures file (should be done!)

*Sample sizes are after removal of outliers, and refer to the $Rt$ model. Dashes indicate that the variable was available for all records.

@@

![**Figure 3. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b), across species for the three focal droughts.** Species codes are given in Table 2.](tables_figures/publication/Figure3_resistance_across_sp.png)

![3b](tables_figures/publication/Figure3_resilience_across_sp.png)

>>>>

*Sample sizes are after removal of outliers. Dashes indicate that the variable was available for all records. For resistance, sample sizes of independent variables to the $Rt$ model.

@@

![**Figure 3. Drought resistance, $Rt$ (a), and resilience, $Rs$ (b), across species for the three focal droughts.** Species codes are given in Table 2.](tables_figures/publication/Figure3_Rt-Rs_across_sp.png)
